Fig1

### 2020-05-15 analysis/figure-1.Rmd
now with all three types of comparisons

```{r supplfig-1, fig.width=5, fig.height=5}

@@

s1 <- plot_grid(s1a,s1b,s1c,s1d,s1e,s1f, ncol = 2, rel_heights = c(1,0.9,1.3),
                labels = c("B", "C"), label_size = 8)

supplfig1 <- plot_grid(sa, s1, ncol = 1, rel_heights = c(0.75,2), labels = c("A"), label_size = 8)
supplfig1

pdf(file="../figures/supplfig-1-1.pdf", width=5, height=5)
plot(supplfig1)
dev.off()
```

>>>>

```{r supplfig-1, fig.width=7.25, fig.height=5}

@@

s1g <- makebargraphsuppl(DEGchar, "hypothalamus", NULL, 0, 2000) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())  
s1h <- makebargraphsuppl(DEGchar, "pituitary",NULL, 0, 2000)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())   
s1i <- makebargraphsuppl(DEGchar, "gonad",NULL, 0, 2000) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlevelschar)

s1 <- plot_grid(s1a, s1b, s1g, 
          s1c, s1d, s1h, 
          s1e, s1f, s1i, nrow = 3,
          rel_heights = c(1,0.9,1.3),
          labels = c("A", "B", "C"), label_size = 8, rel_widths = c(1.1,1,1))

supplfig1 <- plot_grid(sa, s1, ncol = 1, rel_heights = c(0.7,2))
supplfig1

pdf(file="../figures/supplfig-1-1.pdf", width=7.25, height=5)
plot(supplfig1)
dev.off()
